StateSpaceModels.jl: a Julia Package for Time-Series Analysis in a State-Space Framework

### 2019-07-07 paper/header.tex
final paper update

\title{StateSpaceModels.jl: a Julia Package for \\ Time-Series Analysis in a State-Space Framework}

\author[1,2]{Raphael Saavedra}
\author[1,2]{Guilherme Bodin}
\author[1,2]{Mario Souto}
\affil[1]{Laboratory of Applied Mathematical Programming and Statistics (LAMPS)}
\affil[2]{Pontifical Catholic University of Rio de Janeiro (PUC-Rio), Brazil}

\keywords{State-space models, time-series analysis, Kalman filter, Monte Carlo simulation, forecasting}

>>>>

\title{StateSpaceModels.jl: a Julia Package for Time-Series Analysis in a State-Space Framework}

\author[1, 2]{Raphael Saavedra}
\author[1, 2]{Guilherme Bodin}
\author[1, 2]{Mario Souto}
\affil[1]{Laboratory of Applied Mathematical Programming and Statistics (LAMPS)}
\affil[2]{Pontifical Catholic University of Rio de Janeiro (PUC-Rio), Brazil}

\keywords{State-space models, time-series analysis, Kalman filter, forecasting, Monte Carlo simulation}
